Submission 1.1

### 2023-08-16 Submission 1.1.tex
Update questions 4 and 5 - Right -> Fool -> Not Right is a contradiction - Contradiction in premises means it's possible to prove A -> !A; NOT that there's no case in which they're all true

                    $\neg A \to B$\\
                    $A$\\
                    \rule{5em}{.5pt}\\
                    $\neg B$
          \end{enumerate}
    \item If I'm right, then I'm a fool. But if I'm a fool, I'm not right. Therefore, I'm no fool. (B 70)
          \begin{enumerate}[(a)]
              \item If I'm right, then I'm a fool.\\
                    If I'm a fool, then I'm not right.\\
                    \rule{15em}{.5pt}\\
                    I'm not a fool.
              \item The argument is not valid, since where both premises are true, it is still possible to be a fool. Since it is not valid, it cannot be sound either.
              \item \textit{A}: I'm right\\
                    \textit{B}: I'm a fool\\

                    $A \to B$\\
                    $B \to \neg A$\\
                    \rule{5em}{.5pt}\\
                    $\neg B$
          \end{enumerate}
    \item If I'm right, then I'm a fool. But if I'm a fool, I'm not right. Therefore, I'm not right. (B 70)
          \begin{enumerate}[(a)]
              \item If I'm right, then I'm a fool.\\
                    If I'm a fool, then I'm not right.\\
                    \rule{15em}{.5pt}\\
                    I'm not right.
              \item The argument is valid, but not sound (the premises are likely untrue).\\
              \textit{Saffron's Commentary: I'm not sure whether or not the premises are contradictory? On one hand, if you're right you're a fool and if you're a fool you're not right doesn't seem to work, but it is possible to be a fool and not right without violating either premise. So it is possible for them to both be true at the same time, I think? Just very strange.}
              \item \textit{A}: I'm right\\
                    \textit{B}: I'm a fool\\

>>>>

                    $\neg A \to B$\\
                    $A$\\
                    \rule{5em}{.5pt}\\
                    $\neg B$
          \end{enumerate}
    \item If I'm right, then I'm a fool. But if I'm a fool, I'm not right. Therefore, I'm no fool. (B 70)
          \begin{enumerate}[(a)]
              \item If I'm right, then I'm a fool.\\
                    If I'm a fool, then I'm not right.\\
                    \rule{15em}{.5pt}\\
                    I'm not a fool.
              \item The argument is neither valid nor sound because the premises form a contradiction. Being right implies being a fool, but being a fool implies being not right, so being right implies being not right.
              \item \textit{A}: I'm right\\
                    \textit{B}: I'm a fool\\

                    $A \to B$\\
                    $B \to \neg A$\\
                    \rule{5em}{.5pt}\\
                    $\neg B$
          \end{enumerate}
    \item If I'm right, then I'm a fool. But if I'm a fool, I'm not right. Therefore, I'm not right. (B 70)
          \begin{enumerate}[(a)]
              \item If I'm right, then I'm a fool.\\
                    If I'm a fool, then I'm not right.\\
                    \rule{15em}{.5pt}\\
                    I'm not right.
              \item Again, the premises form a contradiction and so the argument can't be either valid or sound.\\  
              \textit{Saffron's Commentary: I'm not sure whether or not the premises are contradictory? On one hand, if you're right you're a fool and if you're a fool you're not right doesn't seem to work, but it is possible to be a fool and not right without violating either premise. So it is possible for them to both be true at the same time, I think? Just very strange.\\
              Update: Contradictory means you can prove $A \to \neg A$, regardless of whether or not there is a case where all premises are true.}
              \item \textit{A}: I'm right\\
                    \textit{B}: I'm a fool\\
